---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)
```

# Operational Flexibility, International Civil Society, and China's Overseas NGO Law

<!-- badges: start -->
<!-- badges: end -->

[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
Meng Ye • Andrew Young School of Policy Studies • Georgia State University

---

### `r emoji_glue(":maple::llama:")`: Note on "leaf llama" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.5.0. R version 4.3.0 (2023-04-21).

codename(type = "ubuntu", "CH ingo flexibility")
#> [1] "leaf llama"
```


## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions and Code of Conduct

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
